|

### 2022-12-12 r-report/Paper.Rmd
Added Plot 3

```{r,fig.cap="Figure 2: Kaya Identity China - 2000 - 2019"}
YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

```{r,fig.cap="Figure 3"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

>>>>

```{r,fig.cap="Figure 2: Total Emissions, China by Sector - 1970-2019"}
YEAR_L = 1970
YEAR_U = 2019
GAS = "GHG"
COUNTRY = "China"

source("r-analysis/data_sectors_bycountry.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_sectors_bycountry_stacked_abs.R", local = TRUE, print.eval = TRUE)

```{r,fig.cap="Figure 3: Kaya Identity China - 2000 - 2019"}
YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@
